\documentclass[../../Problems]{subfiles}
\begin{document}
{\scriptsize
\subsection{Case Converter}
\textbf{Problem Statement:}\\
Convert a given text into different cases as mentioned below
\begin{description}
	\item[aLtErNaTiNg CaPs] Start with a lower case letter and then keep switching between upper case and lower case letters alternatingly.
	\item[Capitalize Word] Capitalize the first letter of each word and convert all other letters of that word to lower case.
	\item[lower case] Convert every alphabet to lower case.
	\item[Sentence case] Capitalize the first letter of each sentence and convert all other letters of that sentence to lower case. Assume that the sentence only ends with a full stop (`.') .
	\item[tOGGLE cASE] Uncapitalize the first letter of each word and convert all other letters of that word to upper case.
	\item[UPPER CASE] Convert every alphabet to upper case.
\end{description}
\begin{note}
	In all above cases, ignore non-alphabetic characters.
\end{note}
\begin{testcases}
	{sentence\_length\quad x \hfill(x is either a/c/l/s/t/u denoting the case to convert to or e for all cases)\\
	sentence\hfill(entire sentence in a line, the sentence\_length includes spaces)}
	{The sentence converted into x case\hfill{(already taken care of in \href{https://github.com/paramrathour/CS-101/tree/main/Starter Codes/Case Converter.cpp}{Starter Code})}}
	{$1 \leq \text{sentence\_length} \leq 10000$}
	{479\quad e\\The Earth is a very small stage in a vast cosmic arena. Think of the endless cruelties visited by the inhabitants of one corner of this pixel on the scarcely distinguishable inhabitants of some other corner, how frequent their misunderstandings, how eager they are to kill one another, how fervent their hatreds. Think of the rivers of blood spilled by all those generals and emperors so that, in glory and triumph, they could become the momentary masters of a fraction of a dot.}
	{tHe EaRtH iS a VeRy SmAlL sTaGe In A vAsT cOsMiC aReNa. ThInK oF tHe EnDlEsS cRuElTiEs ViSiTeD bY tHe InHaBiTaNtS oF oNe CoRnEr Of ThIs PiXeL oN tHe ScArCeLy DiStInGuIsHaBlE iNhAbItAnTs Of SoMe OtHeR cOrNeR, hOw FrEqUeNt ThEiR mIsUnDeRsTaNdInGs, HoW eAgEr ThEy ArE tO kIlL oNe AnOtHeR, hOw FeRvEnT tHeIr HaTrEdS. tHiNk Of ThE rIvErS oF bLoOd SpIlLeD bY aLl ThOsE gEnErAlS aNd EmPeRoRs So ThAt, In GlOrY aNd TrIuMpH, tHeY cOuLd BeCoMe ThE mOmEnTaRy MaStErS oF a FrAcTiOn Of A dOt.\\\\
The Earth Is A Very Small Stage In A Vast Cosmic Arena. Think Of The Endless Cruelties Visited By The Inhabitants Of One Corner Of This Pixel On The Scarcely Distinguishable Inhabitants Of Some Other Corner, How Frequent Their Misunderstandings, How Eager They Are To Kill One Another, How Fervent Their Hatreds. Think Of The Rivers Of Blood Spilled By All Those Generals And Emperors So That, In Glory And Triumph, They Could Become The Momentary Masters Of A Fraction Of A Dot.\\\\
the earth is a very small stage in a vast cosmic arena. think of the endless cruelties visited by the inhabitants of one corner of this pixel on the scarcely distinguishable inhabitants of some other corner, how frequent their misunderstandings, how eager they are to kill one another, how fervent their hatreds. think of the rivers of blood spilled by all those generals and emperors so that, in glory and triumph, they could become the momentary masters of a fraction of a dot.\\\\
The earth is a very small stage in a vast cosmic arena. Think of the endless cruelties visited by the inhabitants of one corner of this pixel on the scarcely distinguishable inhabitants of some other corner, how frequent their misunderstandings, how eager they are to kill one another, how fervent their hatreds. Think of the rivers of blood spilled by all those generals and emperors so that, in glory and triumph, they could become the momentary masters of a fraction of a dot.\\\\
tHE eARTH iS a vERY sMALL sTAGE iN a vAST cOSMIC aRENA. tHINK oF tHE eNDLESS cRUELTIES vISITED bY tHE iNHABITANTS oF oNE cORNER oF tHIS pIXEL oN tHE sCARCELY dISTINGUISHABLE iNHABITANTS oF sOME oTHER cORNER, hOW fREQUENT tHEIR mISUNDERSTANDINGS, hOW eAGER tHEY aRE tO kILL oNE aNOTHER, hOW fERVENT tHEIR hATREDS. tHINK oF tHE rIVERS oF bLOOD sPILLED bY aLL tHOSE gENERALS aND eMPERORS sO tHAT, iN gLORY aND tRIUMPH, tHEY cOULD bECOME tHE mOMENTARY mASTERS oF a fRACTION oF a dOT.\\\\
THE EARTH IS A VERY SMALL STAGE IN A VAST COSMIC ARENA. THINK OF THE ENDLESS CRUELTIES VISITED BY THE INHABITANTS OF ONE CORNER OF THIS PIXEL ON THE SCARCELY DISTINGUISHABLE INHABITANTS OF SOME OTHER CORNER, HOW FREQUENT THEIR MISUNDERSTANDINGS, HOW EAGER THEY ARE TO KILL ONE ANOTHER, HOW FERVENT THEIR HATREDS. THINK OF THE RIVERS OF BLOOD SPILLED BY ALL THOSE GENERALS AND EMPERORS SO THAT, IN GLORY AND TRIUMPH, THEY COULD BECOME THE MOMENTARY MASTERS OF A FRACTION OF A DOT.}
	% {900 e\\I am not crazy! I know he swapped those numbers! I knew it was 1216. One after Magna Carta. As if I could ever make such a mistake. Never. Never! I just - I just couldn't prove it. He - he covered his tracks, he got that idiot at the copy shop to lie for him. You think this is something? You think this is bad? This? This chicanery? He's done worse. That billboard! Are you telling me that a man just happens to fall like that? No! He orchestrated it! Jimmy! He defecated through a sunroof! And I saved him! And I shouldn't have. I took him into my own firm! What was I thinking? He'll never change. He'll never change! Ever since he was 9, always the same! Couldn't keep his hands out of the cash drawer! But not our Jimmy! Couldn't be precious Jimmy! Stealing them blind! And he gets to be a lawyer!? What a sick joke! I should've stopped him when I had the chance! And you - you have to stop him!}
	% {i Am NoT cRaZy! I kNoW hE sWaPpEd ThOsE nUmBeRs! I kNeW iT wAs 1216. OnE aFtEr MaGnA cArTa. As If I cOuLd EvEr MaKe SuCh A mIsTaKe. NeVeR. nEvEr! I jUsT - i JuSt CoUlDn'T pRoVe It. He - He CoVeReD hIs TrAcKs, He GoT tHaT iDiOt At ThE cOpY sHoP tO lIe FoR hIm. YoU tHiNk ThIs Is SoMeThInG? yOu ThInK tHiS iS bAd? ThIs? ThIs ChIcAnErY? hE's DoNe WoRsE. tHaT bIlLbOaRd! ArE yOu TeLlInG mE tHaT a MaN jUsT hApPeNs To FaLl LiKe ThAt? No! He OrChEsTrAtEd It! JiMmY! hE dEfEcAtEd ThRoUgH a SuNrOoF! aNd I sAvEd HiM! aNd I sHoUlDn'T hAvE. i ToOk HiM iNtO mY oWn FiRm! WhAt WaS i ThInKiNg? He'Ll NeVeR cHaNgE. hE'lL nEvEr ChAnGe! EvEr SiNcE hE wAs 9, AlWaYs ThE sAmE! cOuLdN't KeEp HiS hAnDs OuT oF tHe CaSh DrAwEr! BuT nOt OuR jImMy! CoUlDn'T bE pReCiOuS jImMy! StEaLiNg ThEm BlInD! aNd He GeTs To Be A lAwYeR!? wHaT a SiCk JoKe! I sHoUlD'vE sToPpEd HiM wHeN i HaD tHe ChAnCe! AnD yOu - YoU hAvE tO sToP hIm!\\
	% I Am Not Crazy! I Know He Swapped Those Numbers! I Knew It Was 1216. One After Magna Carta. As If I Could Ever Make Such A Mistake. Never. Never! I Just - I Just Couldn't Prove It. He - He Covered His Tracks, He Got That Idiot At The Copy Shop To Lie For Him. You Think This Is Something? You Think This Is Bad? This? This Chicanery? He's Done Worse. That Billboard! Are You Telling Me That A Man Just Happens To Fall Like That? No! He Orchestrated It! Jimmy! He Defecated Through A Sunroof! And I Saved Him! And I Shouldn't Have. I Took Him Into My Own Firm! What Was I Thinking? He'll Never Change. He'll Never Change! Ever Since He Was 9, Always The Same! Couldn't Keep His Hands Out Of The Cash Drawer! But Not Our Jimmy! Couldn't Be Precious Jimmy! Stealing Them Blind! And He Gets To Be A Lawyer!? What A Sick Joke! I Should've Stopped Him When I Had The Chance! And You - You Have To Stop Him!\\
	% i am not crazy! i know he swapped those numbers! i knew it was 1216. one after magna carta. as if i could ever make such a mistake. never. never! i just - i just couldn't prove it. he - he covered his tracks, he got that idiot at the copy shop to lie for him. you think this is something? you think this is bad? this? this chicanery? he's done worse. that billboard! are you telling me that a man just happens to fall like that? no! he orchestrated it! jimmy! he defecated through a sunroof! and i saved him! and i shouldn't have. i took him into my own firm! what was i thinking? he'll never change. he'll never change! ever since he was 9, always the same! couldn't keep his hands out of the cash drawer! but not our jimmy! couldn't be precious jimmy! stealing them blind! and he gets to be a lawyer!? what a sick joke! i should've stopped him when i had the chance! and you - you have to stop him!\\
	% I am not crazy! i know he swapped those numbers! i knew it was 1216. One after magna carta. As if i could ever make such a mistake. Never. Never! i just - i just couldn't prove it. He - he covered his tracks, he got that idiot at the copy shop to lie for him. You think this is something? you think this is bad? this? this chicanery? he's done worse. That billboard! are you telling me that a man just happens to fall like that? no! he orchestrated it! jimmy! he defecated through a sunroof! and i saved him! and i shouldn't have. I took him into my own firm! what was i thinking? he'll never change. He'll never change! ever since he was 9, always the same! couldn't keep his hands out of the cash drawer! but not our jimmy! couldn't be precious jimmy! stealing them blind! and he gets to be a lawyer!? what a sick joke! i should've stopped him when i had the chance! and you - you have to stop him!\\
	% i aM nOT cRAZY! i kNOW hE sWAPPED tHOSE nUMBERS! i kNEW iT wAS 1216. oNE aFTER mAGNA cARTA. aS iF i cOULD eVER mAKE sUCH a mISTAKE. nEVER. nEVER! i jUST - i jUST cOULDN'T pROVE iT. hE - hE cOVERED hIS tRACKS, hE gOT tHAT iDIOT aT tHE cOPY sHOP tO lIE fOR hIM. yOU tHINK tHIS iS sOMETHING? yOU tHINK tHIS iS bAD? tHIS? tHIS cHICANERY? hE'S dONE wORSE. tHAT bILLBOARD! aRE yOU tELLING mE tHAT a mAN jUST hAPPENS tO fALL lIKE tHAT? nO! hE oRCHESTRATED iT! jIMMY! hE dEFECATED tHROUGH a sUNROOF! aND i sAVED hIM! aND i sHOULDN'T hAVE. i tOOK hIM iNTO mY oWN fIRM! wHAT wAS i tHINKING? hE'LL nEVER cHANGE. hE'LL nEVER cHANGE! eVER sINCE hE wAS 9, aLWAYS tHE sAME! cOULDN'T kEEP hIS hANDS oUT oF tHE cASH dRAWER! bUT nOT oUR jIMMY! cOULDN'T bE pRECIOUS jIMMY! sTEALING tHEM bLIND! aND hE gETS tO bE a lAWYER!? wHAT a sICK jOKE! i sHOULD'VE sTOPPED hIM wHEN i hAD tHE cHANCE! aND yOU - yOU hAVE tO sTOP hIM!\\
	% I AM NOT CRAZY! I KNOW HE SWAPPED THOSE NUMBERS! I KNEW IT WAS 1216. ONE AFTER MAGNA CARTA. AS IF I COULD EVER MAKE SUCH A MISTAKE. NEVER. NEVER! I JUST - I JUST COULDN'T PROVE IT. HE - HE COVERED HIS TRACKS, HE GOT THAT IDIOT AT THE COPY SHOP TO LIE FOR HIM. YOU THINK THIS IS SOMETHING? YOU THINK THIS IS BAD? THIS? THIS CHICANERY? HE'S DONE WORSE. THAT BILLBOARD! ARE YOU TELLING ME THAT A MAN JUST HAPPENS TO FALL LIKE THAT? NO! HE ORCHESTRATED IT! JIMMY! HE DEFECATED THROUGH A SUNROOF! AND I SAVED HIM! AND I SHOULDN'T HAVE. I TOOK HIM INTO MY OWN FIRM! WHAT WAS I THINKING? HE'LL NEVER CHANGE. HE'LL NEVER CHANGE! EVER SINCE HE WAS 9, ALWAYS THE SAME! COULDN'T KEEP HIS HANDS OUT OF THE CASH DRAWER! BUT NOT OUR JIMMY! COULDN'T BE PRECIOUS JIMMY! STEALING THEM BLIND! AND HE GETS TO BE A LAWYER!? WHAT A SICK JOKE! I SHOULD'VE STOPPED HIM WHEN I HAD THE CHANCE! AND YOU - YOU HAVE TO STOP HIM!}
	{https://github.com/paramrathour/CS-101/tree/main/Starter Codes/Case Converter.cpp}
\end{testcases}
}
\end{document}